Reading Notes

### 2020-08-25 2pd.tex
new image for nrel data
* added SQ limit citation

*needs more work
added recent opv papers
fixing up figure positioning etc

%%<why do opvs matter>
The global climate crisis is one of the most pressing issue humanity faces today.
\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/dou-miller2018c-fig.pdf}
    \caption{Schematic showing (a) roll to roll printing process for OPVs, (b) example OPV device, (c) bulk heterojunction structure, and (d) OPV energy generation process. Part (a) adapted from ref \cite{Dou2013}. Parts (b)-(d) adapted from ref \cite{Miller2018c}.}
    \label{fig:opv}
\end{wrapfigure}
Consumption of fossil fuels for energy and transportation strongly contributes to atmospheric $CO_2$ the affects of which are global, long-term, and devastating\cite{Solomon2009a}.
%% should I put examples? fires https://science2017.globalchange.gov/chapter/8/
In our technology-driven society, it is unrealistic to think that energy demand will lessen, in fact global energy consumption is predicted to increase from 17 TW in 2010 to 27 TW in 2040\cite{Mazzio2015}.
In order to protect our climate, we need a non-polluting, cost-efficient way to provide electricity.
Harnessing solar energy is an important part of a green energy solution.
Renewable energy accounted for 11\% of the U.S. energy consumption in 2019 and of that 9\% was from solar (solar accounted for approximately 1\% of the total energy)\cite{USEIA2020}.
Our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar\cite{Wirth2017}.
Traditionally, photovoltaic devices, which can convert incedent light into electric current, were made of inorganic materials like silicon.
But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative\cite{Tang1986b}.
The advantage of OPVs over inorganic PV devices is that OPVs are lightweight, low cost, easier to produce, and flexible. 
OPVs can be manufactured large scale in a roll to roll printing process, similar to newspaper as shown in \autoref{fig:opv} a\cite{Dou2013}.
However, other materials still outperform OPVs (see Figure \ref{fig:nrel}) and in order to become a viable, cost-effective option OPVs need to be more efficient\cite{Mazzio2015}.

\begin{figure}[h!]
    \includegraphics[width=0.9\linewidth]{images/NREL2020.pdf}
    \caption{Efficiencies of all photovoltaic technologies from 1976 to present. OPVs are denoted by red filled circles. The current state-of-the-art OPV research cell achieves 17.4\% efficiency. Image taken from ref \cite{NREL2020}.}
    \label{fig:nrel}
\end{figure}
%% TODO
%% opvs are vast
%% crystalline silicon levels off -- shottkey quessar (sp?) limit 34% efficient not much room for growth (blue)
%% what you can buy vs champion devices
%% opvs show room to grow
%% paying for themselves
%%underdog
In order to make the most efficient OPVs we need to find the blend of compounds and processing conditions that result in the best structure for those compounds.
The active layer of an OPV is mixture of electron-donor and acceptor compounds: the ideal morphology is a micro phase-separated interpenetrating network called a bulk heterojunction (BHJ) (see Figure \ref{fig:opv} c).
The performance of an OPV device is intimately linked with the structure of the active layer:
With minor modifications, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.

% TODO
%% include fig of ITIC PTB7? p3ht, fullerene recent uptick with NFAs
%% look up the 17% solar cell--whats in it?
%% freedom in choosing our ingredients - can we get better than trial and error
Imagine, you are a chemist synthesizing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor, ITIC, and a polymer donor, PTB7. 
Each compound costs \$500 for 100 mg\cite{sigmaaldrich}.
The solvent you use and the concentrations of your active compounds changes the device performance\cite{Hoppe2004a}.
The amount of time the solvent is allowed to evaporate changes the device performance\cite{Li2007}.
The time and temperature of the thermal annealing changes the device performance\cite{Ma2005}.
The regioregularity of your polymer affects the device performance\cite{Kim2006}.
The distribution of polymer lengths affects the device performance\cite{Zhao2013b}.
Changing the functional groups on ITIC changes how it packs in a crystal, its electron affinity, and thus its performance in a device\cite{Swick2019a}.
All this would be to determine the performance of just one donor/acceptor combination in one category of potential compounds\cite{Dou2013}.
This is where molecular simulation can help.
By using a simulation pipeline, we can help to streamline the process of determining which OPV materials will form the best morphology with the best charge transport, and in turn, help to solve the energy crisis.

@@

The performance of an OPV device can be quantified by many metrics.
%% <what is PCE>
The power conversion efficiency (PCE or sometimes $\eta_{e}$) is the ratio of electrical power produced by the device over the power of incedent photons.
Higher PCE means the device is more efficient.  
The material properties which determine the PCE of a device are those which affect the number of photons absorbed, excitons dissociated, and free charges that reach the electrode.
The absorption efficiency depends on the absorption spectrum, absorption coefficient, and layer thickness.
The fraction of excitons which dissociate depends on the exciton dissociation length and the charge separation probability at the interface.
Finally, the the number of charges which reach the electrode depends on the driving force or gradient resulting from the potentials of the electrons and holes\cite{Hoppe2004}.
%%<is there a citation for why charge transport is a good proxy for PCE?>

@@

\begin{wrapfigure}{L}{0.5\linewidth}
    \centering
    \includegraphics[width=0.6\linewidth]{images/ITIC.pdf}
    \caption{ITIC chemical structure with \textcolor{red}{electron accepting regions in red} and \textcolor{blue}{electron donating regions in blue}}
    \label{fig:itic}
\end{wrapfigure}

The planar acceptor-donor-acceptor moeity seen in many NFA backbones (see Figure \ref{fig:itic}) may have more efficient exciton splitting, as compared to a fullerene acceptor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer\cite{Yi2018a}.

@@

%%<md in general>
MD separates the interactions between particles into non-bonded interactions and bond, angle, and dihedral interactions.
Non-bonded interactions are commonly modelled with a Lennard-Jones potential:
$$ U_{LJ}(r_{i,j}) = 4\epsilon\big[\big(\frac{\sigma}{r_{i,j}}\big)^{12}-\big(\frac{\sigma}{r_{i,j}}\big)^{6}\big]$$
Where $i$ and $j$ are the particles separated by distance $r_{i,j}$.
The equilibrium distance between particles is controlled by $\sigma$ and the depth of the potential well is controlled by $\epsilon$ (see Figure \ref{fig:lj}).
A distance cutoff, $r_{cut}$, is often used to reduce the number of pairwise interactions and improve performance.

\begin{wrapfigure}{L}{0.5\linewidth}
    \centering
    \includegraphics[width=0.6\linewidth]{images/lj.pdf}
    \caption{The Lennard-Jones potential with relevant distances labelled}
    \label{fig:lj}
\end{wrapfigure}

Particles connected by bonds are also modelled by classical forces, for example the bond potential may be treated as a harmonic oscillator:

\begin{wrapfigure}{L}{0.5\linewidth}
    \centering
    \includegraphics[width=0.4\linewidth]{images/bondangledihedral.pdf}
    \caption{Bonded interactions: bond (top left), angle (top right), and dihedral (bottom). Image adapted from \cite{punma}.}
    \label{fig:bad}
\end{wrapfigure}

$$V_{bond}(r) = \frac{1}{2}k(r-r_{0})^{2}$$
Where $r$ is the bond length, $r_{0}$ is the equilibrium bond length, and $k$ is the spring constant for the bond.
The angle potential is also treated as a harmonic oscillator:
$$V_{angle}(\theta)=\frac{1}{2}k(\theta-\theta_{0})^{2}$$
Where $\theta$ is the angle formed between three bonded particles, $\theta_{0}$ is the equilibrium angle, and $k$ is the spring contant for the angle.
The dihedral potential can be defined by the follow Fourier series:
$$V_{dihedral}(\phi)=\frac{1}{2}k_{1}(1-cos(\phi))+\frac{1}{2}k_{2}(1-cos(2\phi))+\frac{1}{2}k_{3}(1-cos(3\phi))\frac{1}{2}k_{4}(1-cos(4\phi))$$
Where $\phi$ is the angle between planes formed by particles in the dihedral (see Figure \ref{fig:bad}) and $k_{n}$ are the force coeffients.

@@

When using the MS IBI method, it is important to choose dissimilar states to minimize the potential overlap region.
If this overlap region is large, there are many potentials which will provide matching RDFs.

\begin{wrapfigure}{L}{0.5\linewidth}
    \centering
    \includegraphics[width=0.6\linewidth]{images/moorefig.pdf}
    \caption{Visualization of the state space coverage of different potentials: if the thermodynamic states are too similar (b), then the overlap region is large enough that there are many potentials which will fit the target. Choosing states which are different (a) will better define the potential. Image taken from ref \cite{Moore2014}.}
    \label{fig:lj}
\end{wrapfigure}

@@

My prior work has involved probing the intermolecular interactions which govern dimer and crystal formation.
% With lan - About excitonic splitting, using DFT, DNA. 
An investigation of the excitonic splitting observed in cyanine dye dimers was done using density functional theory (DFT)\cite{Fothergill2018}.
By comparing calculated with experimental absorption spectra it was found that the solvent may play a large role in the dimer formation and peak shifting.
% With Matt - What intermolecular interactions guide diphenylurea crystal formation
An investigation of the supramolecular interactions which guide crystal self-assembly in diphenylurea transition metal complexes was done using density functional theory\cite{Millard2019a}. 
% With us - Perspective paper about all things
My contributions to our perspective paper were mostly about my experience joining the lab and trying to reproduce an existing model; a task which should be very straightforward in a computational field but which any computational scientist can attest is far from simple\cite{Jankowski2019}. 
 %% frame gixstapose as a tool for reproducible, approachable science
I also presented a tool I've developed, called GIXStapose, at the Scientific Python conference (SciPy2020). %%cite scipy and gixstapose
GIXStapose is an interactive structure viewer alongside its simulated diffraction pattern.
This work had two goals: helping users to see the connections between a structure and it's diffraction pattern and making reproducible figure generation easier.
The first goal is achieved through a graphical user interface (GUI) which allows users to interact with the structure using the mouse and the diffraction pattern is updated automatically.
The second goal is accomplished by allowing all steps of the figure generation process (e.g., positioning the camera, setting the colors and lighting, etc) to be scripted and never \textit{requiring} use of the GUI.
These prior works, although not directly related to OPVS or coarse grain models, have helped me think about how atomic interactions can shape a structure, the struggles that face a new computational scientist, and how I can help.

@@

\begin{wrapfigure}{L}{0.5\linewidth}
    \centering
    \includegraphics[width=0.6\linewidth]{images/hexane-compare.pdf}
    \caption{top: hexane chemical structure, bottom: hexane overlaid with coarse grain mapping \textcolor{blue}{A}-\textcolor{orange}{B}-}\textcolor{blue}{A}
    \label{fig:hexane}
\end{wrapfigure}

@@

\begin{wrapfigure}{L}{0.5\linewidth}
    \centering
    \includegraphics[width=0.6\linewidth]{images/hexanexml.pdf}
    \caption{XML file used by VOTCA to specify a three site coarse grain mapping of n-hexane}
    \label{fig:hexanexml}
\end{wrapfigure}

It may be easy to think that because the goal is simple, mapping two carbons and their attached hydrogens to a single bead so that six alkyl carbons becomes three coarse grain sites (A-B-A), that the process will also be simple.
In order to specify a bead-mapping using VOTCA, we need to know the residue number, the residue name, and the atom name.
For a six atom system this is not too bad, but it could get tedious and error-prone for larger systems.
And keep in mind that these xml files need to be created manually for each compound which is coarse grained or  backmapped.
VOTCA's scheme also requires that the bonding and the angles resulting from those bonds are specified, another process which is tedious, error-prone, and probably unecessary. 
To explain, let's discuss my proposed alternative:
\begin{lstlisting}
hexane_sites = [("_A", "C[CH3]"), ("_B", "CC")]
\end{lstlisting}
The result of using this code in the `coarse` function is a three-site hexane model A-B-A, same as VOTCA.%%<link to grits>
The mapping here is specified as a list of bead name SMARTS string pairs.
Although they do add some element of cognitive load, SMARTS strings are designed to be human and machine readable and can match atoms based on their chemical environment.
With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (in SMARTS notation a capital "C" denotes an alkyl carbon) and requiring that one be a terminal carbon by including that it has three attached hydrogens ("[CH3]").
The order of the beads here matters because technically all the carbon atoms in hexane could be mapped with the more general SMARTS string (CC), so it is important to list the most specific strings first.
The bonding and angles of the resulting coarse grain beads can then inferred based on the bonding of the mapped atoms.
Basically what VOTCA's xml file does in 51 lines, I can do in 1 which is easier to read and makes chemical sense. 
There are even benefits to the mapping being inline with the code:
It allows the user to see the mapping as they progress through the workflow without having to search for multiple files.
Not using an external file may prevent common errors caused by manual file IO such as operating system specific line endings or whitespace characters like tab or space being read differently by a program.
Having the mapping in-line with the workflow also allows for the user to check that the mapping is correct with built in interactive visualizations, which can display the mapping as an overlay. 
(Figure \ref{hexane-compare} is the output of one such visualization using py3Dmol.) %%cite py3Dmol

@@

My plan is to create a workflow which builds on existing tools: signac, freud, mbuild, openbabel, and a previously developed msibi package.
This workflow could start with equilibrated atomistic trajectories from multiple statepoints, then use SMARTS strings to map the CG sites to each trajectory and calculate the effective potentials using MSIBI.
Once we have a tabulated coarse grain force field, we can create a larger simulation using our coarse grain model.
Finally, once we have an equilibrated coarse grain trajectory, we can using backmapping to regain the atomic positions and do analysese such as radial distribution function (RDF), charge transport, and diffraction.
If this workflow is streamlined, it can be applied to many different compounds allowing for a high-throughput analysis of many potential OPV compounds.

@@

\section*{Timeline for Implementation and Evaluation}
\begin{table}[h]
    \resizebox{\columnwidth}{!}{
%\resizebox{\textwidth}{!}
    %\centering
    \renewcommand{\arraystretch}{1.1}
    \begin{tabular}{| c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c |}
        \hline
        \multirow{2}{*}{PROJECT TASK}& \multicolumn{4}{c}{YEAR 1} &  \multicolumn{4}{|c}{YEAR 2} & \multicolumn{4}{|c}{YEAR 3} & \multicolumn{4}{|c|}{YEAR 4} & \multicolumn{4}{c|}{YEAR 5} \\ 
        \hhline{~--------------------}
             & 1  & 2  & 3  & 4  & 1  & 2  & 3  & 4  & 1  & 2  & 3  & 4  & 1  & 2  & 3  & 4 & 1  & 2  & 3  & 4\\
        \hline
           Complete Coursework & \multicolumn{10}{|c|}{ {\cellcolor{lgray}} } &  &  &  &  &  &  &  &  &  &\\
        \hline
           Present at a Conference  &  &  &  &  &  &  &  &  &  &  & x &  &  &  &  &  &  &  &  &\\
        \hline
           Publish a First Author Paper  &  &  &  &  &  & x  &  &  &  &  &  &  &  &  &  &  &  &  &  &\\
        \hline
           Proposal and Comprehensive Exam  &  &  &  &  &  &  &  &  &  &  &  & * &  &  &  &  &  &  &  &\\
        \hline
           Expand Functionality of Open Source Packages & & & & & & \multicolumn{11}{|c|}{{\cellcolor{lgray}}} & & & &\\
        \hline
           Develop Coarse Graining Package              & & & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
        \hline
           Develop Automated MS-IBI Code                & & & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
        \hline
           Develop Backmapping Package                  & & & & & & & & & & & & \multicolumn{5}{|c|}{{\cellcolor{lgray}}}& & & &\\
        \hline
           Generate Coarse-Grain Morphologies           & & & & & & & & & & & & & & \multicolumn{4}{|c|}{{\cellcolor{lgray}}}& & &\\
        \hline
           Evaluate OPV Device Performance & & & & & & & & & & & & & & \multicolumn{4}{|c|}{{\cellcolor{lgray}}} & & &\\
        \hline
           Write Dissertation & & & & & & & & & & & & & & & &{\cellcolor{lgray}}& {\cellcolor{lgray}}& {\cellcolor{lgray}} &  &\\
        \hline
           Present Dissertation Defense  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &&  & {\cellcolor{lgray}} &  &\\
        \hline
             %Saved row template
             %&  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
    \end{tabular}}
    \caption{Anticipated timeline. * indicates right now, X indicates already accomplished.}
\end{table}

>>>>

%%<why do opvs matter>
\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/dou-miller2018c-fig.pdf}
    \caption{Schematic showing (a) roll to roll printing process for OPVs, (b) example OPV device, (c) bulk heterojunction structure, and (d) OPV energy generation process. Part (a) adapted from ref \cite{Dou2013}. Parts (b)-(d) adapted from ref \cite{Miller2018c}.}
    \label{opv}
\end{wrapfigure}

The global climate crisis is one of the most pressing issue humanity faces today.
Consumption of fossil fuels for energy and transportation strongly contributes to atmospheric $CO_2$ the affects of which are global, long-term, and devastating\cite{Solomon2009a}.
%% should I put examples? fires https://science2017.globalchange.gov/chapter/8/
In our technology-driven society, it is unrealistic to think that energy demand will lessen, in fact global energy consumption is predicted to increase from 17 TW in 2010 to 27 TW in 2040\cite{Mazzio2015}.
In order to protect our climate, we need a non-polluting, cost-efficient way to provide electricity.
Harnessing solar energy is an important part of a green energy solution.
Renewable energy accounted for 11\% of the U.S. energy consumption in 2019 and of that 9\% was from solar (solar accounted for approximately 1\% of the total energy)\cite{USEIA2020}.
Our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar\cite{Wirth2017}.
Traditionally, photovoltaic devices, which can convert incedent light into electric current, were made of inorganic materials like silicon.
But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative\cite{Tang1986b}.
The advantage of OPVs over inorganic PV devices is that OPVs are lightweight, low cost, easier to produce, and flexible. 
OPVs can be manufactured large scale in a roll to roll printing process, similar to newspaper as shown in \autoref{opv} a\cite{Dou2013}.
However, other materials still outperform OPVs (see \autoref{nrel}) and in order to become a viable, cost-effective option OPVs need to be more efficient\cite{Mazzio2015}.

\begin{figure}[h!]
    \includegraphics[width=\linewidth]{images/NREL2020.pdf}
    \caption{Comparision of efficiencies organic and silicon photovoltaic technologies from 1990 to present. The current state-of-the-art OPV research cell achieves 17.4\% efficiency. Data taken from \cite{NREL2020}.}
    \label{nrel}
\end{figure}

\cite{Lin2019} 17.4 \% efficiency mixing polymer fullerene device with transition metal disulfide.
\cite{Cui2019} champion solar cell chlorinated NFA 16.5\% efiiciency
%% new figure
%% TODO
%% opvs are vast
%% crystalline silicon levels off -- shottkey quessar (sp?) limit 34% efficient not much room for growth (blue)
%% what you can buy vs champion devices
%% opvs show room to grow
%% paying for themselves
%%underdog
In order to make the most efficient OPVs we need to find the blend of compounds and processing conditions that result in the best structure for those compounds.
The active layer of an OPV is mixture of electron-donor and acceptor compounds: the ideal morphology is a micro phase-separated interpenetrating network called a bulk heterojunction (BHJ) (see \autoref{opv} c).
The performance of an OPV device is intimately linked with the structure of the active layer:
With minor modifications, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.

% TODO
%% include fig of ITIC PTB7? p3ht, fullerene recent uptick with NFAs
%% look up the 17% solar cell--whats in it?
%% freedom in choosing our ingredients - can we get better than trial and error
\cite{Cui2019}
chlorinated ladder backbone acceptor 16\% PCE 
%% https://www.printedelectronicsworld.com/articles/15405/raynergy-new-world-record-on-certified-pce-13-28-single-junction-opv
signle junction with NFA

Imagine, you are a chemist synthesizing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor, ITIC, and a polymer donor, PTB7. 
Each compound costs \$500 for 100 mg\cite{sigmaaldrich}.
The solvent you use and the concentrations of your active compounds changes the device performance\cite{Hoppe2004a}.
The amount of time the solvent is allowed to evaporate changes the device performance\cite{Li2007}.
The time and temperature of the thermal annealing changes the device performance\cite{Ma2005}.
The regioregularity of your polymer affects the device performance\cite{Kim2006}.
The distribution of polymer lengths affects the device performance\cite{Zhao2013b}.
Changing the functional groups on ITIC changes how it packs in a crystal, its electron affinity, and thus its performance in a device\cite{Swick2019a}.
All this would be to determine the performance of just one donor/acceptor combination in one category of potential compounds\cite{Dou2013}.
This is where molecular simulation can help.
By using a simulation pipeline, we can help to streamline the process of determining which OPV materials will form the best morphology with the best charge transport, and in turn, help to solve the energy crisis.

@@

The performance of an OPV device can be quantified by many metrics.
%% <what is PCE>
The power conversion efficiency (PCE or sometimes $\eta_{e}$) is the ratio of electrical power produced by the device to the power of incedent photons.
Higher PCE means the device is more efficient.  
The material properties which determine the PCE of a device are those which affect the number of photons absorbed, excitons dissociated, and free charges that reach the electrode.
The absorption efficiency depends on the absorption spectrum, absorption coefficient, and layer thickness.
The fraction of excitons which dissociate depends on the exciton dissociation length and the charge separation probability at the interface.
Finally, the the number of charges which reach the electrode depends on the driving force or gradient resulting from the potentials of the electrons and holes\cite{Hoppe2004}.
%%<is there a citation for why charge transport is a good proxy for PCE?>

@@

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/ITIC.pdf}
    \caption{ITIC chemical structure with \textcolor{red}{electron accepting regions in red} and \textcolor{blue}{electron donating regions in blue}}
    \label{itic}
\end{wrapfigure}

The planar acceptor-donor-acceptor moeity seen in many NFA backbones (see \autoref{itic}) may have more efficient exciton splitting, as compared to a fullerene acceptor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer\cite{Yi2018a}.

@@

%%<md in general>
MD separates the interactions between particles into non-bonded interactions and bond, angle, and dihedral interactions (see \autoref{bad}).

\begin{wrapfigure}{L}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/bondangledihedral.pdf}
    \caption{Bonded interactions: bond (top left), angle (top right), and dihedral (bottom). Image adapted from \cite{punma}.}
    \label{bad}
\end{wrapfigure}

Non-bonded interactions are commonly modelled with a Lennard-Jones potential:
$$ U_{LJ}(r_{i,j}) = 4\epsilon\big[\big(\frac{\sigma}{r_{i,j}}\big)^{12}-\big(\frac{\sigma}{r_{i,j}}\big)^{6}\big]$$
Where $i$ and $j$ are the particles separated by distance $r_{i,j}$.
The equilibrium distance between particles is controlled by $\sigma$ and the depth of the potential well is controlled by $\epsilon$ (see \autoref{lj}).
A distance cutoff, $r_{cut}$, is often used to reduce the number of pairwise interactions and improve performance.

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/lj.pdf}
    \caption{The Lennard-Jones potential with relevant distances labelled}
    \label{lj}
\end{wrapfigure}

Particles connected by bonds are also modelled by classical forces, for example the bond potential may be treated as a harmonic oscillator:
$$V_{bond}(r) = \frac{1}{2}k(r-r_{0})^{2}$$
Where $r$ is the bond length, $r_{0}$ is the equilibrium bond length, and $k$ is the spring constant for the bond.
The angle potential is also treated as a harmonic oscillator:
$$V_{angle}(\theta)=\frac{1}{2}k(\theta-\theta_{0})^{2}$$
Where $\theta$ is the angle formed between three bonded particles, $\theta_{0}$ is the equilibrium angle, and $k$ is the spring contant for the angle.
The dihedral potential can be defined by the follow Fourier series:
$$V_{dihedral}(\phi)=\frac{1}{2}k_{1}(1-cos(\phi))+\frac{1}{2}k_{2}(1-cos(2\phi))+\frac{1}{2}k_{3}(1-cos(3\phi))\frac{1}{2}k_{4}(1-cos(4\phi))$$
Where $\phi$ is the angle between planes formed by particles in the dihedral (see \autoref{bad}) and $k_{n}$ are the force coeffients.

@@

When using the MS IBI method, it is important to choose dissimilar states to minimize the potential overlap region.
If this overlap region is large, there are many potentials which will provide matching RDFs (see \autoref{moore}).

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/moorefig.pdf}
    \caption{Visualization of the state space coverage of different potentials: if the thermodynamic states are too similar (b), then the overlap region is large enough that there are many potentials which will fit the target. Choosing states which are different (a) will better define the potential. Image taken from ref \cite{Moore2014}.}
    \label{moore}
\end{wrapfigure}

@@

My prior work has involved probing the intermolecular interactions which govern dimer and crystal formation.
% With lan - About excitonic splitting, using DFT, DNA. 
An investigation of the excitonic splitting observed in cyanine dye dimers was done using density functional theory (DFT)\cite{Fothergill2018}.
By comparing calculated with experimental absorption spectra it was found that the solvent may play a large role in the dimer formation and peak shifting.
% With Matt - What intermolecular interactions guide diphenylurea crystal formation
An investigation of the supramolecular interactions which guide crystal self-assembly in diphenylurea transition metal complexes was done using density functional theory\cite{Millard2019a}. 
% With us - Perspective paper about all things
My contributions to our perspective paper were mostly about my experience joining the lab and trying to reproduce an existing model; a task which should be very straightforward in a computational field but which any computational scientist can attest is far from simple\cite{Jankowski2019}. 
 %% frame gixstapose as a tool for reproducible, approachable science
I also presented a tool I've developed, called GIXStapose, at the Scientific Python conference (SciPy2020). %%cite scipy and gixstapose
GIXStapose is an interactive structure viewer alongside its simulated diffraction pattern.
This work had two goals: helping users to see the connections between a structure and it's diffraction pattern and making reproducible figure generation easier.
The first goal is achieved through a graphical user interface (GUI) which allows users to interact with the structure using the mouse and the diffraction pattern is updated automatically.
The second goal is accomplished by allowing all steps of the figure generation process (e.g., positioning the camera, setting the colors and lighting, etc) to be scripted and never \textit{requiring} use of the GUI\@.
These prior works, although not directly related to OPVS or coarse grain models, have helped me think about how atomic interactions can shape a structure, the struggles that face a new computational scientist, and how I can help.

@@

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/hexane-compare.pdf}
    \caption{top: hexane chemical structure, bottom: hexane overlaid with coarse grain mapping \textcolor{blue}{A}-\textcolor{orange}{B}-}\textcolor{blue}{A}
    \label{hexane}
\end{wrapfigure}

@@

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/hexanexml.pdf}
    \caption{XML file used by VOTCA to specify a three site coarse grain mapping of n-hexane}
    \label{hexanexml}
\end{wrapfigure}

It may be easy to think that because the goal is simple, mapping two carbons and their attached hydrogens to a single bead so that six alkyl carbons becomes three coarse grain sites (A-B-A), that the process will also be simple.
In order to specify a bead-mapping using VOTCA, we need to know the residue number, the residue name, and the atom name.
For a six atom system this is not too bad, but it could get tedious and error-prone for larger systems.
And keep in mind that these xml files need to be created manually for each compound which is coarse grained or  backmapped.
VOTCA's scheme also requires that the bonding and the angles resulting from those bonds are specified, another process which is tedious, error-prone, and probably unecessary. 
To explain, let's discuss my proposed alternative:
\begin{lstlisting}
hexane_sites = [("_A", "C[CH3]"), ("_B", "CC")]
\end{lstlisting}
The result of using this code in the \lstinline{coarse} function is a three-site hexane model A-B-A, same as VOTCA.%%<link to grits>
The mapping here is specified as a list of bead name SMARTS string pairs.
Although they do add some element of cognitive load, SMARTS strings are designed to be human and machine readable and can match atoms based on their chemical environment.
With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (in SMARTS notation a capital \lstinline{"C"} denotes an alkyl carbon) and requiring that one be a terminal carbon by including that it has three attached hydrogens (\lstinline{"[CH3]"}).
The order of the beads here matters because technically all the carbon atoms in hexane could be mapped with the more general SMARTS string (\lstinline{"CC"}), so it is important to list the most specific strings first.
The bonding and angles of the resulting coarse grain beads can then inferred based on the bonding of the mapped atoms.
Basically what VOTCA's xml file does in 51 lines, I can do in 1 which is easier to read and makes chemical sense. 
There are even benefits to the mapping being inline with the code:
It allows the user to see the mapping as they progress through the workflow without having to search for multiple files.
Not using an external file may prevent common errors caused by manual file IO such as operating system specific line endings or whitespace characters like tab or space being read differently by a program.
Having the mapping in-line with the workflow also allows for the user to check that the mapping is correct with built in interactive visualizations, which can display the mapping as an overlay. 
(\autoref{hexane-compare} is the output of one such visualization using py3Dmol.) %%cite py3Dmol

@@

My plan is to create a workflow which builds on existing tools: signac, freud, mbuild, openbabel, and a previously developed msibi package.
This workflow could start with equilibrated atomistic trajectories from multiple statepoints, then use SMARTS strings to map the CG sites to each trajectory and calculate the effective potentials using MSIBI\@.
Once we have a tabulated coarse grain force field, we can create a larger simulation using our coarse grain model.
Finally, once we have an equilibrated coarse grain trajectory, we can using backmapping to regain the atomic positions and do analysese such as radial distribution function (RDF), charge transport, and diffraction.
If this workflow is streamlined, it can be applied to many different compounds allowing for a high-throughput analysis of many potential OPV compounds.

@@

\section*{Timeline for Implementation and Evaluation}
\begin{table}[h]
    \resizebox{\columnwidth}{!}{
        \renewcommand{\arraystretch}{1.1}
        \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
            \hline
            \multirow{2}{*}{PROJECT TASK}
                &\multicolumn{4}{c}{YEAR 1}
                &\multicolumn{4}{|c}{YEAR 2} 
                &\multicolumn{4}{|c}{YEAR 3} 
                &\multicolumn{4}{|c|}{YEAR 4} 
                &\multicolumn{4}{c|}{YEAR 5} \\ 
            \hhline{~--------------------}
            & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4\\
            \hline
            Complete Coursework 
                &\multicolumn{10}{|c|}{{\cellcolor{lgray}}} &  &  &  &  &  &  &  &  &  &\\
            \hline
            Present at a Conference  
                & & & & & & & & & & & x & & & & & & & & &\\
            \hline
            Publish a First Author Paper
                & & & & & & x & & & & & & & & & & & & & &\\
            \hline
            Proposal and Comprehensive Exam
                & & & & & & & & & & & & * & & & & & & & &\\
            \hline
            Expand Functionality of Open Source Packages 
                & & & & & & \multicolumn{11}{|c|}{{\cellcolor{lgray}}} & & & &\\
            \hline
            Develop Coarse Graining Package              
                & & & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
            \hline
            Develop Automated MS-IBI Code                
                & & & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
            \hline
            Develop Backmapping Package                  
                & & & & & & & & & & & & \multicolumn{5}{|c|}{{\cellcolor{lgray}}}& & & &\\
            \hline
            Generate Coarse-Grain Morphologies           
                & & & & & & & & & & & & & & \multicolumn{4}{|c|}{{\cellcolor{lgray}}}& & &\\
            \hline
            Evaluate OPV Device Performance 
                & & & & & & & & & & & & & & \multicolumn{4}{|c|}{{\cellcolor{lgray}}} & & &\\
            \hline
            Write Dissertation 
                & & & & & & & & & & & & & & & &\multicolumn{3}{|c|}{{\cellcolor{lgray}}} & &\\
            \hline
            Present Dissertation Defense  
                & & & & & & & & & & & & & & & & & & {\cellcolor{lgray}} &  &\\
            \hline
             %Saved row template
             %&  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
        \end{tabular}
    }
    \caption{Anticipated timeline. * indicates right now, x indicates already accomplished.}
\end{table}
